The Astropy Project: \\ Sustaining and Growing a Community-oriented Open-source Project and the Latest Major Release (v5.0) of the Core Package

### 2022-04-19 src/static/authors.tex
final flag
Unify affiliations for SARAO
They were written with the address line in different order. I've used
the version that matches https://www.sarao.ac.za/contact/

\newcommand{\affstsci}{
    Space Telescope Science Institute, 3700 San Martin Drive, Baltimore, MD 21218, USA
}
\newcommand{\affcca}{
    Center for Computational Astrophysics, Flatiron Institute, 162 5th Ave, New York, NY 10010, USA
}
\newcommand{\affcfa}{
    Center for Astrophysics | Harvard \& Smithsonian, 60 Garden Street, Cambridge, MA, 02138, USA
}
\newcommand{\affbaeri}{
    Bay Area Environmental Research Institute, P.O. Box 25, Moffett Field, CA 94035, USA
}
\newcommand{\affprinceton}{
    Department of Astrophysical Sciences, 4 Ivy Lane, Princeton University, Princeton, NJ 08544, USA
}
\newcommand{\affaperio}{
    Aperio Software Ltd., Insight House, Riverside Business Park, Stoney Common Road, Stansted, Essex, CM24 8PL, UK
}
\newcommand{\afftorontoastro}{
    David A. Dunlap Department of Astronomy \& Astrophysics, University of Toronto, 50 St. George Street, Toronto ON M5S 3H4, Canada
}
\newcommand{\affipac}{
    IPAC, MC 100-22, Caltech, 1200E. California Blvd. Pasadena, CA 91125
}
\newcommand{\affcoco}{
    Astropy Coordination Committee
}
\newcommand{\affsteward}{
    Steward Observatory, University of Arizona, 933 North Cherry Avenue, Tucson,
    AZ 85721-0065, USA
}

@@

\author{Bruce~Merry}
\affiliation{South African Radio Astronomy Observatory, 2 Fir Street, Black River Park, Observatory 7925, South Africa}

@@

\author{Ludwig~Schwardt}
\affiliation{South African Radio Astronomy Observatory, Black River Park, 2 Fir Street, Observatory 7925, South Africa}

@@

%FLAG
\author[0000-0002-8310-0829]{Jaladh~Singhal}
\affiliation{TARDIS collaboration}

>>>>

\newcommand{\affstsci}{
    Space Telescope Science Institute, 3700 San Martin Drive, Baltimore, MD 21218, USA
}
\newcommand{\affcca}{
    Center for Computational Astrophysics, Flatiron Institute, 162 5th Ave, New York, NY 10010, USA
}
\newcommand{\affcfa}{
    Center for Astrophysics | Harvard \& Smithsonian, 60 Garden Street, Cambridge, MA, 02138, USA
}
\newcommand{\affbaeri}{
    Bay Area Environmental Research Institute, P.O. Box 25, Moffett Field, CA 94035, USA
}
\newcommand{\affprinceton}{
    Department of Astrophysical Sciences, 4 Ivy Lane, Princeton University, Princeton, NJ 08544, USA
}
\newcommand{\affaperio}{
    Aperio Software Ltd., Insight House, Riverside Business Park, Stoney Common Road, Stansted, Essex, CM24 8PL, UK
}
\newcommand{\afftorontoastro}{
    David A. Dunlap Department of Astronomy \& Astrophysics, University of Toronto, 50 St. George Street, Toronto ON M5S 3H4, Canada
}
\newcommand{\affipac}{
    IPAC, MC 100-22, Caltech, 1200E. California Blvd. Pasadena, CA 91125
}
\newcommand{\affcoco}{
    Astropy Coordination Committee
}
\newcommand{\affsteward}{
    Steward Observatory, University of Arizona, 933 North Cherry Avenue, Tucson,
    AZ 85721-0065, USA
}
\newcommand{\affsarao}{
    South African Radio Astronomy Observatory, 2 Fir Street, Black River Park,
    Observatory 7925, South Africa
}

@@

\author{Bruce~Merry}
\affiliation{\affsarao}

@@

\author{Ludwig~Schwardt}
\affiliation{\affsarao}

@@

\author[0000-0002-8310-0829]{Jaladh~Singhal}
% \affiliation{TARDIS collaboration}
\noaffiliation
